### 2016-04-07 ch02-qlogms/excitation-design.tex
LPM illustration improved
Externalize some frequency grids
 - also computed alpha, delta for example grid.

The $(1,1)$ element of the $\partial G_{1,1}$ entry of the information matrix is
\begin{align}
  \int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
\end{align}
which yields
\begin{equation}
\frac{\pi }
          {16  \sqrt{1 - \damping^2}\wn^{2} \damping^{3}} 
+ 
\frac{ 2\arctan  
                               \left(
                                       \frac{(2  \damping^{2} - 1) \sqrt{1-\damping^{2}}}
                                                {2  (\damping^{3} - \damping)}
                              \right)}
         {16  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
+
\frac{{\left(2  \damping^{2} + 1 \right)} }
         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
\label{eq:excitation:auto:full}
\end{equation}
after lengthy calculations.
For $\damping \ll 1$ this can be simplified to
\begin{equation}
\label{eq:excitation:auto}
\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
 = 
 \frac{\pi}
          {8\wn[1]^2}\damping^{-3} 
+ \bigO{\damping^{-2}}
\end{equation}
since the $\arctan$ in \eqref{eq:excitation:auto:full} tends to $\frac{\pi}{2}$ for $\damping \to 0$.
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
\begin{gather}
\left|\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:excitation:cross1} \\
\leq
\int_0^\infty\left|\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} 
  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.

@@

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \label{fig:excitation:freqGrids}
  \end{figure}

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  %TODO: turn this into a guideline?
  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

>>>>

The $(1,1)$ element of the $\partial G_{1,1}$ entry of the information matrix is
\begin{align}
  \int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
\end{align}
which evaluates to
\begin{equation}
\frac{\pi }
          {16  \sqrt{1 - \damping^2}\wn^{2} \damping^{3}} 
+ 
\frac{ 2\arctan  
                               \left(
                                       \frac{(2  \damping^{2} - 1) \sqrt{1-\damping^{2}}}
                                                {2  (\damping^{3} - \damping)}
                              \right)}
         {16  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
+
\frac{{\left(2  \damping^{2} + 1 \right)} }
         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
\label{eq:excitation:auto:full}
\end{equation}
after lengthy calculations.
For $\damping \ll 1$ this can be simplified to
\begin{equation}
\label{eq:excitation:auto}
\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
 = 
 \frac{\pi}
          {8\wn[1]^2}\damping^{-3} 
+ \bigO{\damping^{-2}}
\end{equation}
since the $\arctan$ in \eqref{eq:excitation:auto:full} tends to $\frac{\pi}{2}$ for $\damping \to 0$.
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
\begin{gather}
\left|\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:excitation:cross1} \\
\leq
\int_0^\infty\left|\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} 
  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.

@@

  \begin{figure}[ht]
    \centering
      \remakeNextFigure
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.
    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions. }%
    \label{fig:excitation:freqGrids}
  \end{figure}

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\omegaLinLog, +\infty}$, where
  \begin{equation}
    \omegaLinLog \isdef \frac{2\pi \Delta f}{\alpha - 1}
    \label{eq:excitation:linearLogTransitionFrequency}
  \end{equation}
  indicates the lowest frequency where the quasi-logarithmic grid can effectively reproduce the logarithmic spacing.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  %TODO: turn this into a guideline?
  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.
